Age-related changes in plant growth and traits

### 2015-05-19 results_accessory_shorter.rmd
created separate "RA_schedules_shorter" results file.

* A couple of questions:
    1. What should one measure?
    2. What does it mean as proportional energy shifts between accessory cost pools?

@@

* Looking at proportions, the pattern is much less informative
* Plants with higher RA have lower allocation to pre-pollination tissues, probably because of their higher seedset
```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=7}
par(mfrow=c(1,2), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,.1,0.2))  
mod <- lm(asin(sqrt(RA))~asin(sqrt(PerPrePol_All)),data=subset(SummaryInd,RA>0&PerPrePol_All>0))
plot(asin(sqrt(PerPrePol_All))~asin(sqrt(RA)),data=subset(SummaryInd,RA>0&PerPrePol_All>0), pch=16,col=col.spp[as.factor(species)])
words.top.right(mod)

>>>>

    1. What reproduction "pool" should one measure?
      * Is fecundity good enough?
      * Is fruit or propagule weight good enough?
    2. What might cause shifts in accessory costs across species?
      * Previous studies have shown smaller-seeded species have lower accessory costs.
      * This data set also lets us look at individual pools of accessory tissues and see how they change across species.
    3. How does alotment to different accessory tissue types shift within a species as it ages, grows, or increases RA? 
      * If accessory costs decrease with increased RA, increasing RA yields compounding returns.

@@

* Looking at proportions, the pattern is much less informative
* Plants with higher RA have lower allocation to pre-pollination tissues, probably because of their higher seedset
* Total accessory costs and RA and rather unrelated - the plot shows a significant increase in accessory costs as RA increases, but this is mostly driven by BOLE

```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=7}
par(mfrow=c(1,2), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,.1,0.2))  
mod <- lm(asin(sqrt(RA))~asin(sqrt(PerPrePol_All)),data=subset(SummaryInd,RA>0&PerPrePol_All>0))
plot(asin(sqrt(PerPrePol_All))~asin(sqrt(RA)),data=subset(SummaryInd,RA>0&PerPrePol_All>0), pch=16,col=col.spp[as.factor(species)])
words.top.right(mod)

### 2015-05-19 results_best.Rmd
created separate "RA_schedules_shorter" results file.

```{r, echo=FALSE,message=FALSE, fig.width=12, fig.height=6, out.width=792, out.height=576}
yvar <- "RA"
xvar <- "PropH"

@@

```{r, echo=FALSE,message=FALSE, fig.width=12, fig.height=6, out.width=792, out.height=576}
yvar <- "ReproInv"
xvar <- "PropH"

>>>>

```{r, echo=FALSE,message=FALSE, fig.width=14, fig.height=7}
yvar <- "RA"
xvar <- "PropH"

@@

```{r, echo=FALSE,message=FALSE, fig.width=14, fig.height=7}
yvar <- "ReproInv"
xvar <- "PropH"
